Topological order in the quantum dimer-pentamer model

### 2016-04-29 qdpm_paper.tex
Added some structure factor figures

    In this section we discuss the dimer dimer correlation function
    \begin{equation}
        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
        ,
    \end{equation}
    where $d_i$ is the ising degrees of freedom on link i.
    In order for the QDPM to exhibit topological order there we must find that it is in a gaped
    dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
    we find no evedence of broken symmetries for system sizes up to $32\times32$. As an example of the
    absence of broken symmetries we show
    the dimer correlation function measuered between a single dimer and all other dimers on the
    lattice in Fig.~\ref{fig:fig:dimer_gry_scale_qdpm} for a $16x16$ lattice.
    \subsection{Liquid}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale (actual data) of the dimer corelation between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
        dimers in the upperleft corner are colored red because they are off the scale shown at the
        botom of the figure.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}

    The dimer correlations decay exponetialy in the distance between the dimers. 
    In Fig.~\ref{fig:spacial_dmr_cor} we show the dimer correlations between horizontal dimers
    in a vertical column. We find the correlation length to be $HERE$.
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{spacial_dmr_cor.pdf}
        \caption{(Note: This figure was made using equal probabilities of plaquette flips and
        pentamer moves) Spacial correlation function of parallel dimers for the two different
        sublattices distinguished by their color (red, green).}
        \label{fig:spacial_dmr_cor}
    \end{figure}

>>>>

    In this section we discuss the dimer dimer correlation function
    \begin{equation}
        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
        ,
    \end{equation}
    where $d_i$ represents the presence of a dimer on link i, $1/2$ or $-1/2$ for the presence or
    absence of a dimer respectively.
    In order for the QDPM to exhibit topological order there we must find that it is in a gaped
    dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
    we find no evidence of broken symmetries for system sizes up to $32\times32$. As an example of the
    absence of broken symmetries we show
    the dimer correlation function measured between a single dimer and all other dimers on the
    lattice in Fig.~\ref{fig:fig:dimer_gry_scale_qdpm} for a $16x16$ lattice.
    \subsection{Liquid}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale (actual data) of the dimer correlation between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
        dimers in the upperleft corner are colored red because they are off the scale shown at the
        botom of the figure.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}

    The dimer correlations decay exponentially in the distance between the dimers. 
    In Fig.~\ref{fig:spacial_dmr_cor} we show the dimer correlations between horizontal dimers
    in a vertical column. We find the correlation length to be $HERE$.
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{spacial_dmr_cor.pdf}
        \caption{(Note: This figure was made using equal probabilities of plaquette flips and
        pentamer moves) Spacial correlation function of parallel dimers for the two different
        sublattices distinguished by their color (red, green).}
        \label{fig:spacial_dmr_cor}
    \end{figure}

    %\begin{figure}[htpb]
    %    \centering
    %    \includegraphics[width=0.8\linewidth]{spacial_z3vis_cor.pdf}
    %    \caption{The $Z_3$ vison correlation function for $\gamma=0.5$.}
    %    \label{fig:spacial_z3vis_cor}
    %\end{figure}

    \begin{figure}[htpb]
        \centering
        \includegraphics[width=1.0\linewidth]{qdpm_dmr_HM_16x16.pdf}
        \caption{QDPM dimer structure factor $\gamma=0.5$.}
        \label{fig:spacial_z3vis_cor}
    \end{figure}

    \begin{figure}[htpb]
        \centering
        \includegraphics[width=1.0\linewidth]{qdpm_vis_HM_16x16.pdf}
        \caption{QDPM $Z_3$ vison structure factor $\gamma=0.5$.}
        \label{fig:spacial_z3vis_cor}
    \end{figure}

    \begin{figure}[htpb]
        \centering
        \includegraphics[width=1.0\linewidth]{vis_dmr_qdpm_struc_fac_16x16.pdf}
        \caption{The QDPM dimer structure factor $S_d(k)$ and $Z_3$ vison structure factor $S_v(k)$
        shown along the path in $k$ space connecting the $(0,0)$, to $(\pi,0)$, $(\pi,\pi)$, $(0,0)$
        points for $\gamma=0.5$.}
        \label{fig:vis_dmr_cut}
    \end{figure}
